Comparison of FIA and equally-sized communities

### 2021-04-13 analysis/reports/submission2/appendices/s9_fia_comparison.Rmd

---
title: "Comparison of FIA and equally-sized communities"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    # github_document:
    #    df_print: kable
    #    toc: true
    word_document:
        df_print: kable
        toc: false
---

>>>>

---
title: "Comparison of FIA and equally-sized communities"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
       toc: true
    # word_document:
    #     df_print: kable
    #     toc: false
---
